# Formatting Tips

*You should delete this file from your book and remove `bookdowntips.Rmd` from the `_bookdown.yml` file.

## Code

- Do not show code. This should happen automatically since `echo` is set to `FALSE` in `_common.R`.

## Citations

- Cite all text sources using markdown syntax: $[\text{link text}](\text{url})$

- Cite code sources as comments in your code chunks.

```
# From: https://github.com/pbiecek/ema/blob/master/07-iBreak-Down.Rmd#L255
```

## Math

- Use MathJax / Latex format: [basic intro](https://rmd4sci.njtierney.com/math)

- Enclose in single dollar signs for inline expressions: $a^2 + b^2 = c^2$

- Enclose in double dollar signs for new line centered expressions: $$a^2 + b^2 = c^2$$

- Use [hostmath.com](http://hostmath.com/) for a point and click interface to create LaTeX expressions

## Plots

### Figure size

Set a default plot size by adding:

```
fig.width = 5,
fig.height = 3.5
```

(You can adjust the numbers)

to `knitr::opts_chunk$set()` in `_common.R`.

Then as needed override one or more defaults in particular chunks:

`{r, fig.width=8, fig.height=6}`

In general, faceted plots should have larger sizes.

Examples:

```{r}
library(ggplot2)
ggplot(iris, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() + ggtitle("Default plot size (5 x 3.5)")
```

```{r, fig.width = 3, fig.height = 3, fig.cap=""}
ggplot(iris, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() + ggtitle("In chunk options: \n `fig.width = 3, fig.height = 3`")
```

## Figure numbers

- Include a chunk label *and* a figure caption `fig.cap` in the chunk options:

```
{r hist1, fig.cap = "Histogram of `Sepal.Width`"}
```

- Refer to the plot with the chunk label:

Figure $\text{\@ref(fig:hist1)}$ shows...

```{r hist1, fig.cap = "Histogram of `Sepal.Width`"}
ggplot(iris, aes(Sepal.Width)) + 
  geom_histogram(color = "blue", fill = "cornflowerblue")
```

Figure \@ref(fig:hist1) shows the distribution of `Sepal.Width` in the `iris` dataset.

## Resources

(More will be added)

[Rmarkdown for Scientists](https://rmd4sci.njtierney.com/)
